General Procedure

### 2018-07-17 statement.tex
ihr riecht beide irgendwie seltsam

\section{Walter}

\section{Moritz}

>>>>

\section{Walter \& Moritz}

The two of us grouped up for our contribution to the practicum work. Our task was to research the theoretical backgrounds on the topics "clustering algorithms" and "distance measures". We implemented the gower distance, provided presentation slides and did some coding to test approaches with the generated data from other group members. The latter, among other things, did not result as part of the final submission and we shortened some of our contributions to match the submission requirements. The tasks were equally distributed among us.
